### 2013-08-26 inst/examples/sensitivity-allen.Rmd

```{r stateeq-local}
f <- Myers

@@

```{r sdp-pars, dependson="stateeq-local"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1
x_grid <- seq(0, 1.5 * 6, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  1.7 # observations start from
x0 <- 5 # simulation under policy starts from
Tobs <- 40
MaxT = 1000 # timeout for value iteration convergence
seed <- round(runif(32) * 1e6)
seed[1] <- 1234
seed
```

@@

32 data-sets from the same model

```{r }
yields <- sfSapply(seed, 
function(seed_i){
  set.seed(seed_i)

  p <- c(1.5 + rnorm(1, 0, .1), 2.5 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .2))

  x <- numeric(Tobs)
  x[1] <- Xo
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)

@@

  ## @knitr gp-priors
  s2.p <- c(5,5)  
  d.p = c(10, 1/0.1)

@@

```{r}
ggplot(yields_dat) + geom_density(aes(value, col=simulation)) 
````

```{r}
ggplot(yields_dat) + geom_density(aes(value, col=replicate)) 
````

>>>>

```{r sdp-pars}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1
x_grid <- seq(0, 1.5 * 8, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  5.7 # observations start from
x0 <- 8 # simulation under policy starts from
Tobs <- 40
MaxT = 1000 # timeout for value iteration convergence
````

```{r stateeq-local}
f <- RickerAllee

@@

```{r}
set.seed(12345)
seed <- round(runif(12) * 1e6)
seed
```

@@

Replicate data-sets from the same model

```{r warning=TRUE}
yields <- sfSapply(seed, 
function(seed_i){
  set.seed(seed_i)

  p <- c(2 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .1), 5 + rnorm(1, 0, .2))

  initial_data <- function(){
    x <- numeric(Tobs)
    x[1] <- Xo
    nz <- 1
    for(t in 1:(Tobs-1))
      x[t+1] = z_g() * f(x[t], h=0, p=p)

@@

    out = list(X=X,Y=Y)
    if(x[Tobs-1] < x[1]){
      warning("Training population crashed, trying again")
      out <- initial_data()
    } 
    out
  }

  o <- initial_data()
  X <- o$X; Y <- o$Y
  ## @knitr gp-priors
  s2.p <- c(5,5)  
  d.p = c(10, 1/0.1)

@@

Compare over `r length(seed)` simulation configurations with different parameters and different training data, the GP does consistently well.  Only one case has relatively poor outcomes.

```{r}
ggplot(yields_dat) + geom_density(aes(value, color=as.factor(simulation), fill=as.factor(simulation)), alpha=.5)
````

Within a replicate number, outcomes not that varied over parameters.

```{r}
ggplot(yields_dat) + geom_density(aes(value, group=as.factor(replicate)), alpha=.7)
````
